Bayesian Exploration in Deep Reinforcement Learning

### 2022-09-08 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT
more

\begin{equation}
  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{Z_{\theta}(\rvx,a)}{\hat{\T}
  Z_{\tilde{\theta}}(\rvx,a)}
\end{equation}

@@

\begin{algorithm}
  \caption{Flow-RL Loss}\label{alg:LTM}
  \textbf{Require:} \(N, v, v^{-1}, \theta, \tilde{\theta}\)\\
  \textbf{input} \(\rvx, a, r, \rvx^\prime, \gamma\)\\
  \hspace*{1em} {\color{gray} \# Take \(N\) samples from the value distribution.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} \(\epsilon_i \sim \N \left(0, I_{\lvert \A \rvert} \right)\)\\
  \hspace*{2em} \textbf{for} \(a^\prime \in \A\)\\
  \hspace*{3em} \(Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i \gets v_{\tilde{\theta}}(\epsilon_i; \rvx^\prime)_{a^\prime}\)\\
  \hspace*{2em} \textbf{end}\\
  \hspace*{1em} \textbf{end}\\
  \\\hspace*{1em} {\color{gray} \# Compute greedy next action.}\\
  \hspace*{1em} \(a^* \gets \argmax_{a^\prime} \frac{1}{N} \sum_{i=1}^N Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i\)\\
  \\\hspace*{1em} {\color{gray} \# Calculate loss terms for each sample.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} {\color{gray} \# Apply the distributional Bellman operator.}\\
  \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
  \hspace*{2em} {\color{gray} \# Calculate log-likelihood under \(\N(0,1)\).}\\
  \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 
  \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)^2\)\\
  \hspace*{2em} {\color{gray} \# Calculate log-derivative of \(v^{-1}_\theta\).}\\
  \hspace*{2em} \(\rho_i \gets \log \left\lvert \frac{\partial v_{\theta}^{-1} \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)}{\hat{Z}_{\tilde{\theta}}(\rvx, a)_i} \right\rvert\)\\
  \hspace*{1em} \textbf{end}\\
  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N \delta_i - \rho_i\)
\end{algorithm}

@@

The most popular normalizing flows right now are buildt for large dimensional
spaces such as images. This includes coupling and autoregressive flows. Planar
flow is very easy to turn elementwise, but unfortunately does not have a closed
form inverse for most functions of \(h\). Although it does have one for
piecewise linear funcitons, those do not have second derivative, hence the
gradient of the log absolute determinant would be zero. This would mean it can
not learn appropriate transformations. Instead we define our own flow.

Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
flow, this function is invertible and differentiable given any values for these
parameters. Equation~\ref{eq:luddeflow_inv} and
Equation~\ref{eq:luddeflow_grad} show the closed form gradient.

@@

Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
description is \(w\) changes the slope of the function, \(b\) changes the
\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
vertically.

>>>>

\begin{align}
  \mathcal{L}_{\rvx,a}(\theta) &\defeq \KL{\hat{\T}
  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}\\
  &= \E{\hat{\T} Z_{\tilde{\theta}}(\rvx,a)}{\log \hat{\T}
  Z_{\tilde{\theta}}(\rvx,a) - \log Z_{\theta}(\rvx,a)}\nonumber\\
  &= \E{\hat{\T} Z_{\tilde{\theta}}(\rvx,a)}{- \log Z_{\theta}(\rvx,a)} + const.\nonumber\\
  &\propto -\E{v_\theta^{-1}(\hat{\T} Z_{\tilde{\theta}}(\rvx,a))}{
    \log v^{-1}_\theta \left( \hat{\T} Z_{\tilde{\theta}}(\rvx,a) \right) + \log \left\lvert J_{v_\theta^{-1}}(\rvx, a) \right\rvert}\nonumber
\end{align}

@@

\begin{algorithm}
  \caption{Flow-RL Loss}\label{alg:LTM}
  \textbf{Require:} \(N, v, v^{-1}, \theta, \tilde{\theta}\)\\
  \textbf{input} \(\rvx, a, r, \rvx^\prime, \gamma\)\\
  \hspace*{1em} {\color{gray} \# Take \(N\) samples from the value distribution.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} \(\epsilon_i \sim \N \left(0, I_{\lvert \A \rvert} \right)\)\\
  \hspace*{2em} \textbf{for} \(a^\prime \in \A\)\\
  \hspace*{3em} \(Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i \gets v_{\tilde{\theta}}(\epsilon_i; \rvx^\prime)_{a^\prime}\)\\
  \hspace*{2em} \textbf{end}\\
  \hspace*{1em} \textbf{end}\\
  \\\hspace*{1em} {\color{gray} \# Compute greedy next action.}\\
  \hspace*{1em} \(a^* \gets \argmax_{a^\prime} \frac{1}{N} \sum_{i=1}^N Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i\)\\
  \\\hspace*{1em} {\color{gray} \# Calculate loss terms for each sample.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} {\color{gray} \# Apply the distributional Bellman operator.}\\
  \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
  \hspace*{2em} {\color{gray} \# Calculate negative log-likelihood.}\\
  \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 
  \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)^2\)\\
  \hspace*{2em} {\color{gray} \# Calculate log-derivative of \(v^{-1}_\theta\).}\\
  \hspace*{2em} \(\rho_i \gets \log \left\lvert \frac{\partial v_{\theta}^{-1} \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)}{\hat{Z}_{\tilde{\theta}}(\rvx, a)_i} \right\rvert\)\\
  \hspace*{1em} \textbf{end}\\
  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N huberloss(\delta_i - \rho_i, \epsilon_i)\)
\end{algorithm}

@@

The most popular normalizing flows right now are buildt for large dimensional
spaces such as images. This includes coupling and autoregressive flows. These
will not work for our method, since \(Z_\theta(\rvx, a)\) is a univariate
distribution. Planar flow is also not a good option since it does not have a
closed form inverse 
% Planar
% flow is very easy to turn elementwise, but unfortunately does not have a closed
% form inverse for most functions of \(h\). Although it does have one for
% piecewise linear funcitons, those do not have second derivative, hence the
% gradient of the log absolute determinant would be zero. This would mean it can
% not learn appropriate transformations. Instead we define our own flow.

Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
\(v(z; b, c, d)\), with 3 free parameters \(b, c, d\). Unlike the planar
flow, this function is invertible and differentiable given any values for these
parameters. Equation~\ref{eq:luddeflow_inv} and
Equation~\ref{eq:luddeflow_grad} show the closed form gradient.

@@

Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
description is that \(b\) changes the
\emph{linearity} of the function \(c\) shifts the horizontally, and
\(d\) shifts the function vertically.
